---
title: "RERDDAP-DataPull"
author: "Aaron Mamula"
date: "5/19/2021"
output: html_document
---

Here is some "throw-away" code to test getting bathymetry data from the ```rerddap``` package:


```{r warning=F, message=F}
rm(list=ls())
library(rerddap)
library(dplyr)
library(ggplot2)
```


We can refer to the NOAA Coastwatch ERDDAP portal for some info on a couple bathymetry grids I've used before:

* [NOAA Coastal Relief Model v.6: Southern California](https://coastwatch.pfeg.noaa.gov/erddap/griddap/usgsCeCrm6.html)
* [NOAA Coastal Relief MOdel v.7: Northern California/Southern Oregon](https://coastwatch.pfeg.noaa.gov/erddap/griddap/usgsCeCrm7.html)

```{r}
q <- ed_search(query = "Topography NOAA Coastal Relief")
```

This isn't the most elegant way to do things but I found a data set I'm familiar with in the 8th position of the first list element of the object ```q```:

Now we need to get the actual data:

```{r}
# it pays to use pretty small bounding boxes here is possible.

# this is a little funky because the NOAA Topp for "Northern California/Southern Oregon" stops at 37. If we want Santa Cruz to HMB we 
# need to pull from 2 different Topos

# this is also a little unstable....it might be better to pull the .csv from the CoastWatch web portal...


bathy.df1 <- griddap("usgsCeCrm6", 
                      latitude =  c(36.5, 37),
                      longitude = c(-124, -120))
bathy.df1 <- bathy.df1[[2]]

bathy.df2 <- griddap("usgsCeCrm7", 
                      latitude =  c(37, 37.4),
                      longitude = c(-125, -120))
bathy.df2 <- bathy.df2[[2]]

```




